---
title: "Developing Data Products Pitch"
author: "Martin Halwachs"
date: "6 August 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Idea
Many people have problems understanding various topics in mathematics. To start off, we will show you an important topic within functional theory: The polynomial.

One main property of polynomials is the order `n`.

So view the following plot to see and understand the differences in polynomial order.

## Orders of polynomials
```{r, warning=FALSE, error=FALSE}
library(ggplot2)
x <- seq(from=-1,to=1,by=0.01)
df <- data.frame(x=rep(x,11))
df$y <- unlist(lapply(0:10, function(n){x^n}),recursive=FALSE)
df$order <- as.factor(rep(0:10, each=length(x)))
p <- ggplot(data=df, aes(x=x, y=y, color=order))
p <- p + geom_hline(yintercept=0)
p <- p + geom_vline(xintercept=0)
p <- p + geom_line()
p <- p + scale_y_continuous(limits=c(-1,1))
p <- p + scale_x_continuous(limits=c(-1,1))
p
```

## Code for the plot
```{r, eval=FALSE, echo=TRUE}
library(ggplot2)
x <- seq(from=-1,to=1,by=0.01)
df <- data.frame(x=rep(x,11))
df$y <- unlist(lapply(0:10, function(n){x^n}),recursive=FALSE)
df$order <- as.factor(rep(0:10, each=length(x)))
p <- ggplot(data=df, aes(x=x, y=y, color=order))
p <- p + geom_hline(yintercept=0)
p <- p + geom_vline(xintercept=0)
p <- p + geom_line()
p <- p + scale_y_continuous(limits=c(-1,1))
p <- p + scale_x_continuous(limits=c(-1,1))
p
```

## Interactive Application

Does this plot look complicate?

Are you frustrated by the lack of overview?

Luckily there is now an application providing the overview you need. Check out our new easy to use application at:

https://mjhalwa.shinyapps.io/coursera-developingdataproducts-courseproject/

